---
title: "case_study"
author: "Dylan Morgan"
date: "2024-10-08"
output: github_document
---

```{r}
library(p8105.datasets)
library(tidyverse)
library(dplyr)
library(leaflet)

data(nyc_airbnb)
```


## Brainstorm Questions

* Where are max and min airbnb prices?
  * What are average prices?
  * What factors affect prices?
* Where are prices going up and down over time?
* What's the relationship between number of reviews and average review?
* Does room type affect availability?
* What's the location of the unit?
  * What areas are popular?
  * Popularity = number of units? Average price?
* Are there repeat host?
  * If so, what does that mean?
  
```{r}
nyc_airbnb |> 
  group_by(neighbourhood_group, room_type) |> 
  summarize(mean_price = mean(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```

```{r}
ggplot() + 
  geom_point(data = nyc_airbnb, 
             mapping = 
               aes(x = long, 
                   y = lat, 
                   size = number_of_reviews, 
                   alpha = 1, 
                   color = price))
```

Leaflet
```{r}
pal <- colorNumeric(
  palette = "viridis", 
  domain = nyc_airbnb$review_scores_location
)

nyc_airbnb |> 
  filter(neighbourhood_group == "Manhattan", 
         price < 1000) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, color = ~pal(review_scores_location), radius = 2)
```

